%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%
%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Aniket Singh} \\[7.5pt]
\href{https://github.com/aniketsingh1023}{\raisebox{-0.05\height}\faGithub\ aniketsingh1023} \ $|$ \ 
\href{https://www.linkedin.com/in/aniket-singh-994b34274}{\raisebox{-0.05\height}\faLinkedin\ Aniket Singh} \ $|$ \ 
\href{https://aniket-portfolio-2024.vercel.app/}{\raisebox{-0.05\height}\faGlobe \ aniketsingh.com} \ $|$ \ 
\href{mailto:aniketsinghn10@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ aniketsinghn10@gmail.com} \ $|$ \ 
\href{tel:+919893101074}{\raisebox{-0.05\height}\faMobile \ +91 9893101074} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
\textbf{Data Analyst / AI Engineer and Full-stack developer} with \textbf{1 year} of experience skilled in \textbf{Python }and \textbf{MERN} stack, with experience in \textbf{SQL/NoSQL} databases,\textbf{ cloud platforms}, and hosting. Built scalable systems and SaaS applications. \textbf{Fast learner},\textbf{ adaptable}, and eager to work with new technologies and AI/data-driven solutions. 

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2030 - present & PhD (Subject) at \textbf{University} \hfill \normalsize (GPA: 4.0/4.0) \\

2023 - 2027 & Bachelor's Degree at \textbf{College} \hfill (GPA: 4.0/4.0) \\ 

2022 & Class 12th Some Board \hfill  (Grades) \\

2021 & Class 10th Some Board \hfill  (Grades) \\
\end{tabularx}

%Experience
\section{Work Experience}

\begin{joblong}{\textbf{Python Developer \& Data Analysis Intern}, Botmartz IT Solutions}{Sept 2024 -- Feb 2025}
\item \textbf{Executed} multiple projects including \textbf{Astroshala}, a \textbf{RAG-based chatbot} for astrological predictions using \textbf{Vector DB} and a full pipeline in \textbf{Flask}.
\item \textbf{Developed} scalable websites with \textbf{Flask} and \textbf{FastAPI} backends.  
\item \textbf{Performed} advanced \textbf{data analysis tasks} to support business insights.  
\end{joblong}

% 2nd Work Experience
\begin{joblong}{\textbf{Associate Software Development Intern}, Qualimatrix Technologies}{Mar 2025 -- May 2025}
\item \textbf{Learned and implemented} full-stack development in \textbf{MERN stack}.  
\item \textbf{Contributed} to multiple \textbf{products} with focus on scalability and performance.  
\item \textbf{Integrated AI-driven features}, enhancing applications with intelligent capabilities.  
\end{joblong}

% 3rd Work Experience
\begin{joblong}{\textbf{ Lead Software Development Intern \& Project Lead}, Unjob.ai}{June 2025 -- Present}
\item \textbf{Founded and built} the MVP for the product \textbf{Unjob.ai}, handling end-to-end development.  
\item \textbf{Promoted to Project Lead}, successfully \textbf{managing and mentoring} a team of 5 developers.  
\item \textbf{Led feature development}, optimized workflows, and delivered scalable solutions for SaaS applications.  
\item \textbf{Collaborated} on product strategy, design, and deployment using modern \textbf{full-stack technologies}.  
\end{joblong}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
% Skills
\section{\underline{Technical Skills}} {\footnotesize Last updated: \today}

\begin{itemize}
    \item \textbf{Languages:} Python, JavaScript, TypeScript, SQL
    \item \textbf{Frameworks:} Django, Flask, FastAPI, React, Next.js, Node.js, Express, MERN Stack
    \item \textbf{Databases:} MySQL, PostgreSQL, MongoDB, Vector DBs (Pinecone/FAISS)
    \item \textbf{Cloud \& Hosting:} AWS, Azure, Vercel, Netlify, Docker, GitHub Actions
\end{itemize}




% Projects
\section{\underline{Projects}}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Multi-Class Text Classification using BERT} & \hfill \href{https://github.com/aniketsingh1023/Text-Classification-Using-BERT}{GitHub Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Fine-tuned \textbf{BERT} for \textbf{sentiment analysis}, \textbf{topic classification}, and \textbf{spam detection} with optimized preprocessing and dataset labeling.  
\textbf{Technologies:} Python, BERT, Transformers, PyTorch, NLP} \\[6pt]

\textbf{CI/CD with Azure} & \hfill \href{https://github.com/aniketsingh1023/CICD-with-Azure}{GitHub Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Implemented a robust \textbf{CI/CD pipeline} using \textbf{Azure DevOps} for automated testing, integration, and deployment, ensuring faster and reliable delivery.  
\textbf{Technologies:} Azure DevOps, GitHub, CI/CD Pipelines} \\[6pt]

\textbf{Fyrebit Hackwave (Hackathon Project)} & \hfill \href{https://github.com/aniketsingh1023/Fyrebit-Hackwave}{GitHub Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Developed a \textbf{web scraper} and a \textbf{Next.js full-stack application} during the \textbf{Fyrebit Hackwave Hackathon}, integrating backend services with modern frontend architecture.  
\textbf{Technologies:} Next.js, Node.js, Web Scraping, MongoDB} \\

\end{tabularx}





%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{\underline{Publications}}

\begin{itemize}
  \item \textbf{Polyp Detection in Colonoscopy Images using U-Net Architecture}  
  Healthcare-focused research paper on \textbf{medical image segmentation} for early colorectal cancer detection using \textbf{U-Net deep learning architecture}.  
  Published in \textit{Revista de Tecnología e Innovación}, 2025  
  \href{https://revistastecac.com/index.php/TEC/article/view/523}{Read Publication}
\end{itemize}

\section{\underline{Achievements}}

\begin{itemize}
    % Open Source
    \item \textbf{Open Source Contributions:}  
    Completed \textbf{Hacktoberfest 2024 (all levels)} and contributed as a \textbf{GSSoC Contributor 2025}.  

    % Problem Solving + Freelancing
    \item \textbf{Problem Solving \& Freelancing:}  
    Solved \textbf{200+ coding problems} across platforms. Active freelancer with \textbf{10+ projects delivered} successfully to clients.  

    % Hackathons / Competitions
    \item \textbf{Hackathons \& Competitions:}  
    Winner at \textbf{Hackndore Hackathon}.  
    Winner of \textbf{Frontend Battle, IIT Bhubaneswar}.  
    Secured \textbf{AIR 1 at BAJA}, for building an \textbf{autonomous buggy vehicle}.  

    % Soft Skills / Leadership
    \item \textbf{Leadership \& Soft Skills:}  
    Lead of \textbf{IPS Tech Club}, organizing \textbf{200+ events}, including hackathons and TEDx-scale conferences. Recognized for strong \textbf{communication, management, and leadership} skills.  
\end{itemize}


\end{document}
